Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
address JA comments section Experiment

Different sets of parameters were tested to compute the MFCCs. Results here are only reported for the best setting, which consisted of $40$ MFCCs (including the first energy coefficient) computed for windows of $50\,\mathrm{ms}$ and hops of $25\,\mathrm{ms}$, with full frequency range. This setting gives us $600$ feature vectors per scene. It has been reported that classifying the each individual frame directly may not be the best approach \cite{rakotomamonjy2015histogram}. \ja{Why?} In order to reduce the amount of data, a pooling step is performed on the MFCCs: each recording is divided into $n$ non-overlapping $t$-seconds long ``texture'' windows. The MFCC vectors within each texture window are then averaged in time. As the \emph{ob} approaches involve a clustering step, we need to ensure that both MFCCs and scattering coefficients have a comparable number of vectors per recording. \ja{Why do we need to do this?} Thus, $t$ is set to $250\,\mathrm{ms}$, resulting in $120$ MFCCs texture windows per scene.

>>>>

Different sets of parameters were tested to compute the MFCCs. Results here are only reported for the best setting, which consisted of $40$ MFCCs (including the first energy coefficient) computed for windows of $50\,\mathrm{ms}$ and hops of $25\,\mathrm{ms}$, with full frequency range. This setting gives us $600$ feature vectors per scene. To get a more robust representation of lower dimensionality a pooling step is performed on the MFCCs: each recording is divided into $n$ non-overlapping $t$-seconds long ``texture'' windows. The MFCC vectors within each texture window are then averaged in time. As the \emph{ob} approaches involve a clustering step, we need to ensure that both MFCCs and scattering coefficients have a comparable number of vectors per recording. \ja{Why do we need to do this?} Thus, $t$ is set to $250\,\mathrm{ms}$, resulting in $120$ MFCCs texture windows per scene.
